\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-21 paper.tex
admission control

Firstly, we advocate traffic engineering with \textit{bandwidth availability} (\textit{BA}) provision: 
a \textit{BA} demand $(b_d, \beta_d, t_d^s, t_d^e)$ means that it requests bandwidth $b_d$ for a life duration between $ t_d^s$ and $t_d^e$, and should be guaranteed at least $\beta_d\%$ of the duration, subjected to the network capacity and possible failures. Such a demand is typically represented by a Service Level Agreement (see Table \ref{target} for real world examples), and different users or applications may pose different demands. 
%a tenant's \textit{promised bandwidth of service $j$ should be available at least $\beta_j\%$ time}.  
%It tries to guarantee the bandwidth demands from tenants under network uncertainty.
We show that state-of-the-art traffic engineering schemes fail to meet the heterogeneous bandwidth  availability demands, especially under diverse link failure probabilities that may vary by several orders of magnitude (see $\S$\ref{background}). We note that, although the general concept of bandwidth-based availability has been recognized in some recent TE works \cite{hong2018b4,bwe, B4}, their methodologies and evaluations are actually achieving only a soft guarantee, i.e., the ratio of the allocated bandwidth to the negotiated one, while we will provide a hard guarantee, i.e., the negotiated bandwidth must be met.

@@

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in the set of s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
\hline
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\multirow{3}{*}{$(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{a BA demand, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
\hline
$D, D_a$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$D_a$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$d_{ik}$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

\textbf{BA demand model:}
We model the inter-DC WAN as a  graph $G=(V,E)$,  where $V$ and $E$ are nodes and link sets.
Let $K$ denote the a source and destination DC pair.
%Each link $e\in E$ is associated with a link capacity $c_e$ (e.g., in bps).
%DC pair set is $K$ and  $\beta_j$ presents the desired availability target  of service $j \in J$.
%\multirow{3}{*}{$d_i=(\mathbf{b}_i, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b}_i$ with }\\
%&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b}_i$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
%&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
A  bandwidth availability demand can be presented as $(\mathbf{b}_d, \beta_d,t_d^s,t_d^e)$,
where $\mathbf{b}_d$ is a vector $<\mathbf{b}_d^1, \mathbf{b}_d^2, ...>$ of bandwidth demands over all s-d pairs.
%where $\alpha$ and $\delta$ are the arrival and departure of the demand, $\gamma$ denotes the service type and $\theta =\{d_{1}, d_{2}, ...,d_{K} \}$ presents bandwidth over each node pair.
%We assume one tenant can only start one service and if a tenant wants to boot multiple services, we can use multiple tuples to describe it.
Network providers will offer refunding for any violating availability targets (see $\S$\ref{background}) and we use $h_d$ to denote the profit (after refunding) for demand $d$.
%The system should reserve enough bandwidth to guarantee all \textit{admitted} requests' availability demands.
%When all services'  \textit{achieved} bandwidth-based availability are larger than their corresponding desired availability target, the system is able to accommodate this service request, otherwise, the request will be denied.

@@

\textbf{Controller} is the brain of the whole system. It is responsible for allocating WAN level bandwidth, and orchestrates all activities with a global view. The four main components in Controller are as follows.
(1) Offline Routing.
This module maintains the WAN level network topology, and computes TE tunnels between each node pair
 (i.e., $T_k,\forall \text{s-d pair} k \in K$), using certain routing algorithms (oblivious routing \cite{SMORE}, k-shortest path \cite{swan}, etc.). 
 %When topology changes (e.g., remove a node) are reported to controller, the TE Routing module will perform routing algorithm (oblivious routing \cite{SMORE}, k-shortest path \cite{swan}, etc.) to derive all the possible tunnels between each node pair (i.e., $T_k,\forall k \in K$) offline.
These tunnels are used by the admission control module and the online scheduler module as input variables;
(2) Admission Control.
When a BA demand is submitted, this module uses the admission control algorithm (see $\S$ \ref{admission_control}) to reject it, or accept it and allocate bandwith over the tunnels in nearly real-time.
The results are sent to the corresponding brokers.
(3) Online Scheduler. 
Periodically, This module performs traffic scheduling (see $\S$ \ref{TE}) according to the bandwidth availability demands submitted by users, so that the availability can be optimized in an expected manner. 
It also pre-computes backup allocation (see $\S$ \ref{backup}) for some potential link failures.
For each user demand, the normal bandwidth and backup bandwidth allocated over each tunnel (i.e., $f_i^t$) are then sent to the corresponding brokers. 
In addition, our system also supports several other TE algorithms including SWAN \cite{swan}, FFC \cite{FFC} and TEAVAR \cite{TEAVAR}.
(4) Communication Channel.
This module is responsible for communication with brokers, where we use long-lived TCP connections to avoid unnecessary delay. 
In addition, controller failures can be remedied by using multiple replications, 
where the master controller is elected by the Paxos \cite{lamport1998the} algorithm.
%To handle controller failure, the controller also replicate controllers and places them in different data centers, then Paxos \cite{lamport1998the} is used to elect one controller as the master.

@@

\textbf{Broker} takes cares of the corresponding data center. It consists of  three modules:
%(1) Demand  Aggregator.
%After receiving demands from hosts, brokers will aggregate them according to service over each node pair (i.e., $d_{jk}$).
%They are sent to controller along with the availability targets of each service (i.e., $\beta_j$);
%%The necessary information includes the application identifier, source address, destination address and expected bandwidth demand.
%Demand Collector gathers traffic demands and aggregates them on the basis of  flow identifiers (i.e., $ < AppID,Src,Dst >$);
%(2) \textit{Demand Predictior}.
%In $\mathsf{Dionysus}$ framework, resources should be able to be dynamic allocated according to the demands of applications.
%However, future application bandwidth demands can't be known beforehand, which makes it hard to adjust in real-time.
%The broker keeps the empirical demands collected by Demand Collector.
%With these history data, 
%Demand Predictior will predict the future bandwidth demands with data-driven algorithms such as ARIMA\cite{ARMA}, reinforcement learning \cite{Pensieve}; 
(1) Bandwidth Enforcer.
It receives the bandwidth allocation results (i.e., $f_i^t$) from controller, sends them to the corresponding hosts, and limits the actual traffic rate in each tunnel in case something is wrong on the end hosts;
(2) Network Agent.
We use commodity SDN switches at data center edges to connect DCs into an Inter-DC WAN.
The network agent runs in a SDN controller (we use floodlight \cite{floodlight}), 
and uses the OpenFlow \cite{openflow} protocol to installs and updates forwarding rules 
on the switches in the same DC. 
To reduce rule complexity, our system uses a label-based forwarding scheme, 
where the first 12 bits of a VxLAN ID represent different demands, 
and the last 12 bits represent different tunnels.
Therefore, 4096 demands and 4096 tunnels can be supported simultaneously, 
which can be further expanded if necessary. 
In this way, a flow (i.e., traffic corresponding to a BA demand) is marked with a label at the ingress switch, and the succeeding switches use this label for forwarding.
Group tables in the switch pipelines are used for flow splitting (i.e., traffic corresponding to a BA demand 
can be split into multiple sub-flows and transmitted in multiple tunnels).
%Flow table just maps the packet based on the destination and the group tables consist of bandwidth weight for each label.
Besides, the network agent also tracks the network topology, reports any change or failure to the central Controller module, and monitors the actual traffic rate. 
(3) Communication Channel.
This component is responsible for communication with the central Controller.
%In reality, many switches are able to detect link failure  \cite{FDT,olfd}.
%Brokers exploit this and send the failure information to controller after the edge switches detect link failures.

>>>>

Firstly, we advocate traffic engineering with \textit{bandwidth availability} (\textit{BA}) provision: 
 $(b_d, \beta_d, t_d^s, t_d^e)$ means that a BA demand $d$ requests bandwidth $b_d$ for a life duration between $ t_d^s$ and $t_d^e$, and should be guaranteed at least $\beta_d\%$ of the duration, subjected to the network capacity and possible failures. Such a demand is typically represented by a Service Level Agreement (see Table \ref{target} for real world examples), and different users or applications may pose different demands. 
%a tenant's \textit{promised bandwidth of service $j$ should be available at least $\beta_j\%$ time}.  
%It tries to guarantee the bandwidth demands from tenants under network uncertainty.
We show that state-of-the-art traffic engineering schemes fail to meet the heterogeneous bandwidth  availability demands, especially under diverse link failure probabilities that may vary by several orders of magnitude (see $\S$\ref{background}). We note that, although the general concept of bandwidth-based availability has been recognized in some recent TE works \cite{hong2018b4,bwe, B4}, their methodologies and evaluations are actually achieving only a soft guarantee, i.e., the ratio of the allocated bandwidth to the negotiated one, while we will provide a hard guarantee, i.e., the negotiated bandwidth must be met.

@@

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{BATE}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in the set of s-d pairs}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
\hline
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
$D, D_a$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$D_a$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
\hline
\multirow{3}{*}{$(\mathbf{b}_d, \beta_d)$}&\multicolumn{6}{|l}{for a BA demand $d$, requiring bandwidth $\mathbf{b}_d$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_d$, where $\mathbf{b}_d$ is a vector $<\mathbf{b}^1_d, \mathbf{b}^2_d, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
%\hline
%$D, D_a$&\multicolumn{6}{|l}{the set of arrived demands and admitted demands\footnote{$D_a$ will update every time slot and an admitted demand will be removed if it finishes.} }\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$d_{ik}$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

@@

\textbf{BA demand model:}
We model the inter-DC WAN as a  graph $G=(V,E)$,  where $V$ and $E$ are nodes and link sets.
Let $K$ denote the a source and destination DC pair.
%Each link $e\in E$ is associated with a link capacity $c_e$ (e.g., in bps).
%DC pair set is $K$ and  $\beta_j$ presents the desired availability target  of service $j \in J$.
%\multirow{3}{*}{$d_i=(\mathbf{b}_i, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b}_i$ with }\\
%&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b}_i$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
%&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
For a  bandwidth availability demand $d$, the BA abstraction can be presented as $(\mathbf{b}_d, \beta_d,t_d^s,t_d^e)$,
where $\mathbf{b}_d$ is a vector $<\mathbf{b}_d^1, \mathbf{b}_d^2, ...>$ of bandwidth demands over all s-d pairs.
%where $\alpha$ and $\delta$ are the arrival and departure of the demand, $\gamma$ denotes the service type and $\theta =\{d_{1}, d_{2}, ...,d_{K} \}$ presents bandwidth over each node pair.
%We assume one tenant can only start one service and if a tenant wants to boot multiple services, we can use multiple tuples to describe it.
Network providers will offer refunding for any violating availability targets (see $\S$\ref{background}) and we use $h_d$ to denote the profit (after refunding) for demand $d$.
%The system should reserve enough bandwidth to guarantee all \textit{admitted} requests' availability demands.
%When all services'  \textit{achieved} bandwidth-based availability are larger than their corresponding desired availability target, the system is able to accommodate this service request, otherwise, the request will be denied.

@@

\textbf{Controller} is the brain of the whole system. It is responsible for allocating WAN level bandwidth, and orchestrates all activities with a global view. The four main components in Controller are as follows.
(1) Offline Routing.
This module maintains the WAN level network topology, and computes TE tunnels between each node pair
 (i.e., $T_k,\forall \text{s-d pair} k \in K$), using certain routing algorithms (oblivious routing \cite{SMORE}, k-shortest path \cite{swan}, etc.). 
 %When topology changes (e.g., remove a node) are reported to controller, the TE Routing module will perform routing algorithm (oblivious routing \cite{SMORE}, k-shortest path \cite{swan}, etc.) to derive all the possible tunnels between each node pair (i.e., $T_k,\forall k \in K$) offline.
These tunnels are used by the admission control module and the online scheduler module as input variables;
(2) Admission Control.
When a BA demand is submitted, this module uses the admission control algorithm (see $\S$ \ref{admission_control}) to reject it, or accept it and allocate bandwith over the tunnels in nearly real-time.
The results are sent to the corresponding brokers.
(3) Online Scheduler. 
Periodically, This module performs traffic scheduling (see $\S$ \ref{TE}) according to the bandwidth availability demands submitted by users, so that the availability can be optimized in an expected manner. 
It also pre-computes backup allocation (see $\S$ \ref{backup}) for some potential link failures.
For each user demand, the normal bandwidth and backup bandwidth allocated over each tunnel (i.e., $f_i^t$) are then sent to the corresponding brokers. 
In addition, our system also supports several other TE algorithms including SWAN \cite{swan}, FFC \cite{FFC} and TEAVAR \cite{TEAVAR}.
(4) Communication Channel.
This module is responsible for communication with brokers, where we use long-lived TCP connections to avoid unnecessary delay. 
In addition, controller failure can be avoided by using multiple replications, 
where the master controller is elected by the Paxos \cite{lamport1998the} algorithm.
%To handle controller failure, the controller also replicate controllers and places them in different data centers, then Paxos \cite{lamport1998the} is used to elect one controller as the master.

@@

\textbf{Broker} is take cares of the corresponding data center. It consists of  two modules:
%(1) Demand  Aggregator.
%After receiving demands from hosts, brokers will aggregate them according to service over each node pair (i.e., $d_{jk}$).
%They are sent to controller along with the availability targets of each service (i.e., $\beta_j$);
%%The necessary information includes the application identifier, source address, destination address and expected bandwidth demand.
%Demand Collector gathers traffic demands and aggregates them on the basis of  flow identifiers (i.e., $ < AppID,Src,Dst >$);
%(2) \textit{Demand Predictior}.
%In $\mathsf{Dionysus}$ framework, resources should be able to be dynamic allocated according to the demands of applications.
%However, future application bandwidth demands can't be known beforehand, which makes it hard to adjust in real-time.
%The broker keeps the empirical demands collected by Demand Collector.
%With these history data, 
%Demand Predictior will predict the future bandwidth demands with data-driven algorithms such as ARIMA\cite{ARMA}, reinforcement learning \cite{Pensieve}; 
(1) Bandwidth Enforcer.
It receives the bandwidth allocation results (i.e., $f_i^t$) from controller, sends them to the corresponding hosts, and limits the actual traffic rate in each tunnel in case something is wrong on the end hosts;
(2) Network Agent.
We use commodity SDN switches at data center edges to connect DCs into an Inter-DC WAN.
The network agent runs in a SDN controller (we use floodlight \cite{floodlight}), 
and uses the OpenFlow \cite{openflow} protocol to installs and updates forwarding rules 
on the switches in the same DC. 
To reduce rule complexity, our system uses a label-based forwarding scheme, 
where the first 12 bits of a VxLAN ID represent different demands, 
and the last 12 bits represent different tunnels.
Therefore, 4096 demands and 4096 tunnels can be supported simultaneously, 
which can be further expanded if necessary. 
In this way, a flow (i.e., traffic corresponding to a BA demand) is marked with a label at the ingress switch, and the succeeding switches use this label for forwarding.
Group tables in the switch pipelines are used for flow splitting (i.e., traffic corresponding to a BA demand 
can be split into multiple sub-flows and transmitted in multiple tunnels).
%Flow table just maps the packet based on the destination and the group tables consist of bandwidth weight for each label.
Besides, the network agent also tracks the network topology, reports any change or failure to the central Controller module, and monitors the actual traffic rate. 
(3) Communication Channel.
This component is responsible for communication with the central Controller.
%In reality, many switches are able to detect link failure  \cite{FDT,olfd}.
%Brokers exploit this and send the failure information to controller after the edge switches detect link failures.
